Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-05-08 tese2/evaluation.tex
[ADD] chapter summary
[RFT] scaling options, on tests

With this results we conclude that if we want to scale our solution's storage using the \emph{MongoDB}'s cluster configuration, both \emph{Kurento Repository} and \emph{MongoDB} should be installed in the same machine because the loopback interface can handle bigger transfer rates than the remaining network interfaces. For the same reason another possible configuration for scaling the storage is to install both \emph{Kurento Repository} and \ac{KMS} on the same machine.

@@

In this chapter we describe the test scenarios that we have created in order to evaluate our system.

>>>>

With this results we conclude that if we want to scale our solution's storage using the \emph{MongoDB}'s cluster configuration, both \emph{Kurento Repository} and \emph{MongoDB} should be installed in the same machine because the loopback interface can handle bigger transfer rates than the remaining network interfaces as seen on figure \ref{fig:scale1}. For the same reason another possible configuration for scaling the storage is to install both \emph{Kurento Repository} and \ac{KMS} on the same machine as seen on figure \ref{fig:scale2}. Installing the repository on the same machine as a database node does not ensure that recorded videos are stored in the same machine, for this reason we would prefer installing \ac{KMS} and \emph{Kurento Repository} on the same machine.

\begin{figure}[!htb]
\centering
\begin{minipage}[b]{0.45\linewidth}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/scale1.pdf}
  \caption{Repository and database in the same machine}
  \label{fig:scale1}
\end{minipage}
\quad
\begin{minipage}[b]{0.45\linewidth}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/scale2.pdf}
  \caption{Repository and KMS in the same machine}
  \label{fig:scale2}
\end{minipage}
\end{figure}

@@

In this chapter we described the test scenarios that we have created in order to evaluate our system.
